Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra using Murchison Widefield Array Observations

### 2015-04-29 ms.tex
Switch from using eor.bib to included bbl info
From ddeba41:
============

In ms.tex,

(*) Switch from using eor.bib to included bbl info

% \par\bigskip
\bibliographystyle{apj}
\bibliography{eor}

% \begin{thebibliography}{}
% \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

% \bibitem[{{Ali} {et~al.}(2008){Ali}, {Bharadwaj}, \& {Chengalur}}]{ali08}
% {Ali}, S.~S., {Bharadwaj}, S., \& {Chengalur}, J.~N. 2008, \mnras, 385, 2166

% \bibitem[{{Beardsley} {et~al.}(2013){Beardsley}, {Hazelton}, {Morales},
%   {Arcus}, {Barnes}, {Bernardi}, {Bowman}, {Briggs}, {Bunton}, {Cappallo},
%   {Corey}, {Deshpande}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
%   {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kincaid},
%   {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter}, {Mitchell},
%   {Morgan}, {Oberoi}, {Ord}, {Pathikulangara}, {Prabu}, {Remillard}, {Rogers},
%   {Roshi}, {Salah}, {Sault}, {Udaya}, {Srivani}, {Stevens}, {Subrahmanyan},
%   {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams},
%   \& {Wyithe}}]{bea13}
% {Beardsley}, A.~P., {Hazelton}, B.~J., {Morales}, M.~F., {et~al.} 2013, \mnras,
%   429, L5

% \bibitem[{{Bernardi} {et~al.}(2009){Bernardi}, {de Bruyn}, {Brentjens},
%   {Ciardi}, {Harker}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
%   {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber09}
% {Bernardi}, G., {de Bruyn}, A.~G., {Brentjens}, M.~A., {et~al.} 2009, \aap,
%   500, 965

% \bibitem[{{Bernardi} {et~al.}(2010){Bernardi}, {de Bruyn}, {Harker},
%   {Brentjens}, {Ciardi}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
%   {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber10}
% {Bernardi}, G., {de Bruyn}, A.~G., {Harker}, G., {et~al.} 2010, \aap, 522, A67

% \bibitem[{{Bowman} {et~al.}(2006){Bowman}, {Morales}, \& {Hewitt}}]{bow06}
% {Bowman}, J.~D., {Morales}, M.~F., \& {Hewitt}, J.~N. 2006, \apj, 638, 20

% \bibitem[{{Bowman} {et~al.}(2009){Bowman}, {Morales}, \& {Hewitt}}]{bow09}
% ---. 2009, \apj, 695, 183

% \bibitem[{{Bowman} {et~al.}(2013){Bowman}, {Cairns}, {Kaplan}, {Murphy},
%   {Oberoi}, {Staveley-Smith}, {Arcus}, {Barnes}, {Bernardi}, {Briggs}, {Brown},
%   {Bunton}, {Burgasser}, {Cappallo}, {Chatterjee}, {Corey}, {Coster},
%   {Deshpande}, {deSouza}, {Emrich}, {Erickson}, {Goeke}, {Gaensler},
%   {Greenhill}, {Harvey-Smith}, {Hazelton}, {Herne}, {Hewitt},
%   {Johnston-Hollitt}, {Kasper}, {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale},
%   {Lynch}, {Matthews}, {McWhirter}, {Mitchell}, {Morales}, {Morgan}, {Ord},
%   {Pathikulangara}, {Prabu}, {Remillard}, {Robishaw}, {Rogers}, {Roshi},
%   {Salah}, {Sault}, {Shankar}, {Srivani}, {Stevens}, {Subrahmanyan}, {Tingay},
%   {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams}, \&
%   {Wyithe}}]{bow13}
% {Bowman}, J.~D., {Cairns}, I., {Kaplan}, D.~L., {et~al.} 2013, \pasa, 30, 31

% \bibitem[{{Datta} {et~al.}(2010){Datta}, {Bowman}, \& {Carilli}}]{dat10}
% {Datta}, A., {Bowman}, J.~D., \& {Carilli}, C.~L. 2010, \apj, 724, 526

% \bibitem[{{Di Matteo} {et~al.}(2004){Di Matteo}, {Ciardi}, \&
%   {Miniati}}]{dim04}
% {Di Matteo}, T., {Ciardi}, B., \& {Miniati}, F. 2004, \mnras, 355, 1053

% \bibitem[{{Di Matteo} {et~al.}(2002){Di Matteo}, {Perna}, {Abel}, \&
%   {Rees}}]{dim02}
% {Di Matteo}, T., {Perna}, R., {Abel}, T., \& {Rees}, M.~J. 2002, \apj, 564, 576

% \bibitem[{Dillon {et~al.}(2013)Dillon, Liu, \& Tegmark}]{dil13}
% Dillon, J.~S., Liu, A., \& Tegmark, M. 2013, Phys. Rev. D, 87, 043005

% \bibitem[{{Dillon} {et~al.}(2014){Dillon}, {Liu}, {Williams}, {Hewitt},
%   {Tegmark}, {Morgan}, {Levine}, {Morales}, {Tingay}, {Bernardi}, {Bowman},
%   {Briggs}, {Cappallo}, {Emrich}, {Mitchell}, {Oberoi}, {Prabu}, {Wayth}, \&
%   {Webster}}]{dil14}
% {Dillon}, J.~S., {Liu}, A., {Williams}, C.~L., {et~al.} 2014, \prd, 89, 023002

% \bibitem[{{Furlanetto} \& {Briggs}(2004)}]{fur04}
% {Furlanetto}, S.~R., \& {Briggs}, F.~H. 2004, \nar, 48, 1039

% \bibitem[{{Furlanetto} {et~al.}(2006){Furlanetto}, {Oh}, \& {Briggs}}]{fur06}
% {Furlanetto}, S.~R., {Oh}, S.~P., \& {Briggs}, F.~H. 2006, \physrep, 433, 181

% \bibitem[{{Ghosh} {et~al.}(2012){Ghosh}, {Prasad}, {Bharadwaj}, {Ali}, \&
%   {Chengalur}}]{gho12}
% {Ghosh}, A., {Prasad}, J., {Bharadwaj}, S., {Ali}, S.~S., \& {Chengalur}, J.~N.
%   2012, \mnras, 426, 3295

% \bibitem[{{Gleser} {et~al.}(2008){Gleser}, {Nusser}, \& {Benson}}]{gle08}
% {Gleser}, L., {Nusser}, A., \& {Benson}, A.~J. 2008, \mnras, 391, 383

% \bibitem[{{Hurley-Walker} {et~al.}(2014){Hurley-Walker}, {Morgan}, {Wayth},
%   {Hancock}, {Bell}, {Bernardi}, {Bhat}, {Briggs}, {Deshpande}, {Ewall-Wice},
%   {Feng}, {Hazelton}, {Hindson}, {Jacobs}, {Kaplan}, {Kudryavtseva}, {Lenc},
%   {McKinley}, {Mitchell}, {Pindor}, {Procopio}, {Oberoi}, {Offringa}, {Ord},
%   {Riding}, {Bowman}, {Cappallo}, {Corey}, {Emrich}, {Gaensler}, {Goeke},
%   {Greenhill}, {Hewitt}, {Johnston-Hollitt}, {Kasper}, {Kratzenberg},
%   {Lonsdale}, {Lynch}, {McWhirter}, {Morales}, {Morgan}, {Prabu}, {Rogers},
%   {Roshi}, {Shankar}, {Srivani}, {Subrahmanyan}, {Tingay}, {Waterson},
%   {Webster}, {Whitney}, {Williams}, \& {Williams}}]{hur14}
% {Hurley-Walker}, N., {Morgan}, J., {Wayth}, R.~B., {et~al.} 2014, \pasa, 31, 45

% \bibitem[{{Iliev} {et~al.}(2002){Iliev}, {Shapiro}, {Ferrara}, \&
%   {Martel}}]{ili02}
% {Iliev}, I.~T., {Shapiro}, P.~R., {Ferrara}, A., \& {Martel}, H. 2002, \apjl,
%   572, L123

% \bibitem[{{Liu} {et~al.}(2014{\natexlab{a}}){Liu}, {Parsons}, \&
%   {Trott}}]{liu14a}
% {Liu}, A., {Parsons}, A.~R., \& {Trott}, C.~M. 2014{\natexlab{a}}, \prd, 90,
%   023018

% \bibitem[{{Liu} {et~al.}(2014{\natexlab{b}}){Liu}, {Parsons}, \&
%   {Trott}}]{liu14b}
% ---. 2014{\natexlab{b}}, \prd, 90, 023019

% \bibitem[{{Liu} \& {Tegmark}(2011)}]{liu11}
% {Liu}, A., \& {Tegmark}, M. 2011, \prd, 83, 103006

% \bibitem[{{Liu} {et~al.}(2009){Liu}, {Tegmark}, {Bowman}, {Hewitt}, \&
%   {Zaldarriaga}}]{liu09}
% {Liu}, A., {Tegmark}, M., {Bowman}, J., {Hewitt}, J., \& {Zaldarriaga}, M.
%   2009, \mnras, 398, 401

% \bibitem[{{Lonsdale} {et~al.}(2009){Lonsdale}, {Cappallo}, {Morales}, {Briggs},
%   {Benkevitch}, {Bowman}, {Bunton}, {Burns}, {Corey}, {Desouza}, {Doeleman},
%   {Derome}, {Deshpande}, {Gopala}, {Greenhill}, {Herne}, {Hewitt}, {Kamini},
%   {Kasper}, {Kincaid}, {Kocz}, {Kowald}, {Kratzenberg}, {Kumar}, {Lynch},
%   {Madhavi}, {Matejek}, {Mitchell}, {Morgan}, {Oberoi}, {Ord},
%   {Pathikulangara}, {Prabu}, {Rogers}, {Roshi}, {Salah}, {Sault}, {Shankar},
%   {Srivani}, {Stevens}, {Tingay}, {Vaccarella}, {Waterson}, {Wayth}, {Webster},
%   {Whitney}, {Williams}, \& {Williams}}]{lon09}
% {Lonsdale}, C.~J., {Cappallo}, R.~J., {Morales}, M.~F., {et~al.} 2009, IEEE
%   Proceedings, 97, 1497

% \bibitem[{{Madau} {et~al.}(1997){Madau}, {Meiksin}, \& {Rees}}]{mad97}
% {Madau}, P., {Meiksin}, A., \& {Rees}, M.~J. 1997, \apj, 475, 429

% \bibitem[{{McQuinn} {et~al.}(2006){McQuinn}, {Zahn}, {Zaldarriaga},
%   {Hernquist}, \& {Furlanetto}}]{mcq06}
% {McQuinn}, M., {Zahn}, O., {Zaldarriaga}, M., {Hernquist}, L., \& {Furlanetto},
%   S.~R. 2006, \apj, 653, 815

% \bibitem[{{Morales} {et~al.}(2006){Morales}, {Bowman}, \& {Hewitt}}]{mor06}
% {Morales}, M.~F., {Bowman}, J.~D., \& {Hewitt}, J.~N. 2006, \apj, 648, 767

% \bibitem[{{Morales} {et~al.}(2012){Morales}, {Hazelton}, {Sullivan}, \&
%   {Beardsley}}]{mor12}
% {Morales}, M.~F., {Hazelton}, B., {Sullivan}, I., \& {Beardsley}, A. 2012,
%   \apj, 752, 137

% \bibitem[{{Morales} \& {Hewitt}(2004)}]{mor04}
% {Morales}, M.~F., \& {Hewitt}, J. 2004, \apj, 615, 7

% \bibitem[{{Parsons} {et~al.}(2012{\natexlab{a}}){Parsons}, {Pober}, {McQuinn},
%   {Jacobs}, \& {Aguirre}}]{par12a}
% {Parsons}, A., {Pober}, J., {McQuinn}, M., {Jacobs}, D., \& {Aguirre}, J.
%   2012{\natexlab{a}}, \apj, 753, 81

% \bibitem[{{Parsons} {et~al.}(2012{\natexlab{b}}){Parsons}, {Pober}, {Aguirre},
%   {Carilli}, {Jacobs}, \& {Moore}}]{par12b}
% {Parsons}, A.~R., {Pober}, J.~C., {Aguirre}, J.~E., {et~al.}
%   2012{\natexlab{b}}, \apj, 756, 165

% \bibitem[{{Parsons} {et~al.}(2010){Parsons}, {Backer}, {Foster}, {Wright},
%   {Bradley}, {Gugliucci}, {Parashare}, {Benoit}, {Aguirre}, {Jacobs},
%   {Carilli}, {Herne}, {Lynch}, {Manley}, \& {Werthimer}}]{par10}
% {Parsons}, A.~R., {Backer}, D.~C., {Foster}, G.~S., {et~al.} 2010, \aj, 139,
%   1468

% \bibitem[{{Pober} {et~al.}(2013){Pober}, {Parsons}, {Aguirre}, {Ali},
%   {Bradley}, {Carilli}, {DeBoer}, {Dexter}, {Gugliucci}, {Jacobs}, {Klima},
%   {MacMahon}, {Manley}, {Moore}, {Stefan}, \& {Walbrugh}}]{pob13}
% {Pober}, J.~C., {Parsons}, A.~R., {Aguirre}, J.~E., {et~al.} 2013, \apjl, 768,
%   L36

% \bibitem[{{Pober} {et~al.}(2014){Pober}, {Liu}, {Dillon}, {Aguirre}, {Bowman},
%   {Bradley}, {Carilli}, {DeBoer}, {Hewitt}, {Jacobs}, {McQuinn}, {Morales},
%   {Parsons}, {Tegmark}, \& {Werthimer}}]{pob14}
% {Pober}, J.~C., {Liu}, A., {Dillon}, J.~S., {et~al.} 2014, \apj, 782, 66

% \bibitem[{{Santos} {et~al.}(2005){Santos}, {Cooray}, \& {Knox}}]{san05}
% {Santos}, M.~G., {Cooray}, A., \& {Knox}, L. 2005, \apj, 625, 575

% \bibitem[{{Scott} \& {Rees}(1990)}]{sco90}
% {Scott}, D., \& {Rees}, M.~J. 1990, \mnras, 247, 510

% \bibitem[{{Sunyaev} \& {Zeldovich}(1972)}]{sun72}
% {Sunyaev}, R.~A., \& {Zeldovich}, Y.~B. 1972, \aap, 20, 189

% \bibitem[{{Thompson} {et~al.}(2001){Thompson}, {Moran}, \& {Swenson}}]{tho01}
% {Thompson}, A.~R., {Moran}, J.~M., \& {Swenson}, Jr., G.~W. 2001,
%   {Interferometry and Synthesis in Radio Astronomy, 2nd Edition} (Wiley)

% \bibitem[{{Thyagarajan} {et~al.}(2013){Thyagarajan}, {Udaya Shankar},
%   {Subrahmanyan}, {Arcus}, {Bernardi}, {Bowman}, {Briggs}, {Bunton},
%   {Cappallo}, {Corey}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
%   {Hazelton}, {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper},
%   {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter},
%   {Mitchell}, {Morales}, {Morgan}, {Oberoi}, {Ord}, {Pathikulangara},
%   {Remillard}, {Rogers}, {Anish Roshi}, {Salah}, {Sault}, {Srivani}, {Stevens},
%   {Thiagaraj}, {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams},
%   {Williams}, \& {Wyithe}}]{thy13}
% {Thyagarajan}, N., {Udaya Shankar}, N., {Subrahmanyan}, R., {et~al.} 2013,
%   \apj, 776, 6

% \bibitem[{{Thyagarajan} {et~al.}(2015){Thyagarajan}, {Jacobs}, {Bowman},
%   {Barry}, {Beardsley}, {Bernardi}, {Briggs}, {Cappallo}, {Carroll}, {Corey},
%   {de Oliveira-Costa}, {Dillon}, {Emrich}, {Ewall-Wice}, {Feng}, {Goeke},
%   {Greenhill}, {Hazelton}, {Hewitt}, {Hurley-Walker}, {Johnston-Hollitt},
%   {Kaplan}, {Kasper}, {Kim}, {Kittiwisit}, {Kratzenberg}, {Lenc}, {Line},
%   {Loeb}, {Lonsdale}, {Lynch}, {McKinley}, {McWhirter}, {Mitchell}, {Morales},
%   {Morgan}, {Neben}, {Oberoi}, {Offringa}, {Ord}, {Paul}, {Pindor}, {Pober},
%   {Prabu}, {Procopio}, {Riding}, {Rogers}, {Roshi}, {Udaya Shankar}, {Sethi},
%   {Srivani}, {Subrahmanyan}, {Sullivan}, {Tegmark}, {Tingay}, {Trott},
%   {Waterson}, {Wayth}, {Webster}, {Whitney}, {Williams}, {Williams}, {Wu}, \&
%   {Wyithe}}]{thy15}
% {Thyagarajan}, N., {Jacobs}, D.~C., {Bowman}, J.~D., {et~al.} 2015, ArXiv
%   e-prints, arXiv:1502.07596

>>>>

% \par\bigskip
\bibliographystyle{apj}
% \bibliography{eor}

\begin{thebibliography}{}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Ali} {et~al.}(2008){Ali}, {Bharadwaj}, \& {Chengalur}}]{ali08}
{Ali}, S.~S., {Bharadwaj}, S., \& {Chengalur}, J.~N. 2008, \mnras, 385, 2166

\bibitem[{{Beardsley} {et~al.}(2013){Beardsley}, {Hazelton}, {Morales},
  {Arcus}, {Barnes}, {Bernardi}, {Bowman}, {Briggs}, {Bunton}, {Cappallo},
  {Corey}, {Deshpande}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
  {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kincaid},
  {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter}, {Mitchell},
  {Morgan}, {Oberoi}, {Ord}, {Pathikulangara}, {Prabu}, {Remillard}, {Rogers},
  {Roshi}, {Salah}, {Sault}, {Udaya}, {Srivani}, {Stevens}, {Subrahmanyan},
  {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams},
  \& {Wyithe}}]{bea13}
{Beardsley}, A.~P., {Hazelton}, B.~J., {Morales}, M.~F., {et~al.} 2013, \mnras,
  429, L5

\bibitem[{{Bernardi} {et~al.}(2009){Bernardi}, {de Bruyn}, {Brentjens},
  {Ciardi}, {Harker}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
  {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber09}
{Bernardi}, G., {de Bruyn}, A.~G., {Brentjens}, M.~A., {et~al.} 2009, \aap,
  500, 965

\bibitem[{{Bernardi} {et~al.}(2010){Bernardi}, {de Bruyn}, {Harker},
  {Brentjens}, {Ciardi}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
  {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber10}
{Bernardi}, G., {de Bruyn}, A.~G., {Harker}, G., {et~al.} 2010, \aap, 522, A67

\bibitem[{{Bowman} {et~al.}(2006){Bowman}, {Morales}, \& {Hewitt}}]{bow06}
{Bowman}, J.~D., {Morales}, M.~F., \& {Hewitt}, J.~N. 2006, \apj, 638, 20

\bibitem[{{Bowman} {et~al.}(2009){Bowman}, {Morales}, \& {Hewitt}}]{bow09}
---. 2009, \apj, 695, 183

\bibitem[{{Bowman} {et~al.}(2013){Bowman}, {Cairns}, {Kaplan}, {Murphy},
  {Oberoi}, {Staveley-Smith}, {Arcus}, {Barnes}, {Bernardi}, {Briggs}, {Brown},
  {Bunton}, {Burgasser}, {Cappallo}, {Chatterjee}, {Corey}, {Coster},
  {Deshpande}, {deSouza}, {Emrich}, {Erickson}, {Goeke}, {Gaensler},
  {Greenhill}, {Harvey-Smith}, {Hazelton}, {Herne}, {Hewitt},
  {Johnston-Hollitt}, {Kasper}, {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale},
  {Lynch}, {Matthews}, {McWhirter}, {Mitchell}, {Morales}, {Morgan}, {Ord},
  {Pathikulangara}, {Prabu}, {Remillard}, {Robishaw}, {Rogers}, {Roshi},
  {Salah}, {Sault}, {Shankar}, {Srivani}, {Stevens}, {Subrahmanyan}, {Tingay},
  {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams}, \&
  {Wyithe}}]{bow13}
{Bowman}, J.~D., {Cairns}, I., {Kaplan}, D.~L., {et~al.} 2013, \pasa, 30, 31

\bibitem[{{Datta} {et~al.}(2010){Datta}, {Bowman}, \& {Carilli}}]{dat10}
{Datta}, A., {Bowman}, J.~D., \& {Carilli}, C.~L. 2010, \apj, 724, 526

\bibitem[{{Di Matteo} {et~al.}(2004){Di Matteo}, {Ciardi}, \&
  {Miniati}}]{dim04}
{Di Matteo}, T., {Ciardi}, B., \& {Miniati}, F. 2004, \mnras, 355, 1053

\bibitem[{{Di Matteo} {et~al.}(2002){Di Matteo}, {Perna}, {Abel}, \&
  {Rees}}]{dim02}
{Di Matteo}, T., {Perna}, R., {Abel}, T., \& {Rees}, M.~J. 2002, \apj, 564, 576

\bibitem[{Dillon {et~al.}(2013)Dillon, Liu, \& Tegmark}]{dil13}
Dillon, J.~S., Liu, A., \& Tegmark, M. 2013, Phys. Rev. D, 87, 043005

\bibitem[{{Dillon} {et~al.}(2014){Dillon}, {Liu}, {Williams}, {Hewitt},
  {Tegmark}, {Morgan}, {Levine}, {Morales}, {Tingay}, {Bernardi}, {Bowman},
  {Briggs}, {Cappallo}, {Emrich}, {Mitchell}, {Oberoi}, {Prabu}, {Wayth}, \&
  {Webster}}]{dil14}
{Dillon}, J.~S., {Liu}, A., {Williams}, C.~L., {et~al.} 2014, \prd, 89, 023002

\bibitem[{{Furlanetto} \& {Briggs}(2004)}]{fur04}
{Furlanetto}, S.~R., \& {Briggs}, F.~H. 2004, \nar, 48, 1039

\bibitem[{{Furlanetto} {et~al.}(2006){Furlanetto}, {Oh}, \& {Briggs}}]{fur06}
{Furlanetto}, S.~R., {Oh}, S.~P., \& {Briggs}, F.~H. 2006, \physrep, 433, 181

\bibitem[{{Ghosh} {et~al.}(2012){Ghosh}, {Prasad}, {Bharadwaj}, {Ali}, \&
  {Chengalur}}]{gho12}
{Ghosh}, A., {Prasad}, J., {Bharadwaj}, S., {Ali}, S.~S., \& {Chengalur}, J.~N.
  2012, \mnras, 426, 3295

\bibitem[{{Gleser} {et~al.}(2008){Gleser}, {Nusser}, \& {Benson}}]{gle08}
{Gleser}, L., {Nusser}, A., \& {Benson}, A.~J. 2008, \mnras, 391, 383

\bibitem[{{Hurley-Walker} {et~al.}(2014){Hurley-Walker}, {Morgan}, {Wayth},
  {Hancock}, {Bell}, {Bernardi}, {Bhat}, {Briggs}, {Deshpande}, {Ewall-Wice},
  {Feng}, {Hazelton}, {Hindson}, {Jacobs}, {Kaplan}, {Kudryavtseva}, {Lenc},
  {McKinley}, {Mitchell}, {Pindor}, {Procopio}, {Oberoi}, {Offringa}, {Ord},
  {Riding}, {Bowman}, {Cappallo}, {Corey}, {Emrich}, {Gaensler}, {Goeke},
  {Greenhill}, {Hewitt}, {Johnston-Hollitt}, {Kasper}, {Kratzenberg},
  {Lonsdale}, {Lynch}, {McWhirter}, {Morales}, {Morgan}, {Prabu}, {Rogers},
  {Roshi}, {Shankar}, {Srivani}, {Subrahmanyan}, {Tingay}, {Waterson},
  {Webster}, {Whitney}, {Williams}, \& {Williams}}]{hur14}
{Hurley-Walker}, N., {Morgan}, J., {Wayth}, R.~B., {et~al.} 2014, \pasa, 31, 45

\bibitem[{{Iliev} {et~al.}(2002){Iliev}, {Shapiro}, {Ferrara}, \&
  {Martel}}]{ili02}
{Iliev}, I.~T., {Shapiro}, P.~R., {Ferrara}, A., \& {Martel}, H. 2002, \apjl,
  572, L123

\bibitem[{{Liu} {et~al.}(2014{\natexlab{a}}){Liu}, {Parsons}, \&
  {Trott}}]{liu14a}
{Liu}, A., {Parsons}, A.~R., \& {Trott}, C.~M. 2014{\natexlab{a}}, \prd, 90,
  023018

\bibitem[{{Liu} {et~al.}(2014{\natexlab{b}}){Liu}, {Parsons}, \&
  {Trott}}]{liu14b}
---. 2014{\natexlab{b}}, \prd, 90, 023019

\bibitem[{{Liu} \& {Tegmark}(2011)}]{liu11}
{Liu}, A., \& {Tegmark}, M. 2011, \prd, 83, 103006

\bibitem[{{Liu} {et~al.}(2009){Liu}, {Tegmark}, {Bowman}, {Hewitt}, \&
  {Zaldarriaga}}]{liu09}
{Liu}, A., {Tegmark}, M., {Bowman}, J., {Hewitt}, J., \& {Zaldarriaga}, M.
  2009, \mnras, 398, 401

\bibitem[{{Lonsdale} {et~al.}(2009){Lonsdale}, {Cappallo}, {Morales}, {Briggs},
  {Benkevitch}, {Bowman}, {Bunton}, {Burns}, {Corey}, {Desouza}, {Doeleman},
  {Derome}, {Deshpande}, {Gopala}, {Greenhill}, {Herne}, {Hewitt}, {Kamini},
  {Kasper}, {Kincaid}, {Kocz}, {Kowald}, {Kratzenberg}, {Kumar}, {Lynch},
  {Madhavi}, {Matejek}, {Mitchell}, {Morgan}, {Oberoi}, {Ord},
  {Pathikulangara}, {Prabu}, {Rogers}, {Roshi}, {Salah}, {Sault}, {Shankar},
  {Srivani}, {Stevens}, {Tingay}, {Vaccarella}, {Waterson}, {Wayth}, {Webster},
  {Whitney}, {Williams}, \& {Williams}}]{lon09}
{Lonsdale}, C.~J., {Cappallo}, R.~J., {Morales}, M.~F., {et~al.} 2009, IEEE
  Proceedings, 97, 1497

\bibitem[{{Madau} {et~al.}(1997){Madau}, {Meiksin}, \& {Rees}}]{mad97}
{Madau}, P., {Meiksin}, A., \& {Rees}, M.~J. 1997, \apj, 475, 429

\bibitem[{{McQuinn} {et~al.}(2006){McQuinn}, {Zahn}, {Zaldarriaga},
  {Hernquist}, \& {Furlanetto}}]{mcq06}
{McQuinn}, M., {Zahn}, O., {Zaldarriaga}, M., {Hernquist}, L., \& {Furlanetto},
  S.~R. 2006, \apj, 653, 815

\bibitem[{{Morales} {et~al.}(2006){Morales}, {Bowman}, \& {Hewitt}}]{mor06}
{Morales}, M.~F., {Bowman}, J.~D., \& {Hewitt}, J.~N. 2006, \apj, 648, 767

\bibitem[{{Morales} {et~al.}(2012){Morales}, {Hazelton}, {Sullivan}, \&
  {Beardsley}}]{mor12}
{Morales}, M.~F., {Hazelton}, B., {Sullivan}, I., \& {Beardsley}, A. 2012,
  \apj, 752, 137

\bibitem[{{Morales} \& {Hewitt}(2004)}]{mor04}
{Morales}, M.~F., \& {Hewitt}, J. 2004, \apj, 615, 7

\bibitem[{{Parsons} {et~al.}(2012{\natexlab{a}}){Parsons}, {Pober}, {McQuinn},
  {Jacobs}, \& {Aguirre}}]{par12a}
{Parsons}, A., {Pober}, J., {McQuinn}, M., {Jacobs}, D., \& {Aguirre}, J.
  2012{\natexlab{a}}, \apj, 753, 81

\bibitem[{{Parsons} {et~al.}(2012{\natexlab{b}}){Parsons}, {Pober}, {Aguirre},
  {Carilli}, {Jacobs}, \& {Moore}}]{par12b}
{Parsons}, A.~R., {Pober}, J.~C., {Aguirre}, J.~E., {et~al.}
  2012{\natexlab{b}}, \apj, 756, 165

\bibitem[{{Parsons} {et~al.}(2010){Parsons}, {Backer}, {Foster}, {Wright},
  {Bradley}, {Gugliucci}, {Parashare}, {Benoit}, {Aguirre}, {Jacobs},
  {Carilli}, {Herne}, {Lynch}, {Manley}, \& {Werthimer}}]{par10}
{Parsons}, A.~R., {Backer}, D.~C., {Foster}, G.~S., {et~al.} 2010, \aj, 139,
  1468

\bibitem[{{Pober} {et~al.}(2013){Pober}, {Parsons}, {Aguirre}, {Ali},
  {Bradley}, {Carilli}, {DeBoer}, {Dexter}, {Gugliucci}, {Jacobs}, {Klima},
  {MacMahon}, {Manley}, {Moore}, {Stefan}, \& {Walbrugh}}]{pob13}
{Pober}, J.~C., {Parsons}, A.~R., {Aguirre}, J.~E., {et~al.} 2013, \apjl, 768,
  L36

\bibitem[{{Pober} {et~al.}(2014){Pober}, {Liu}, {Dillon}, {Aguirre}, {Bowman},
  {Bradley}, {Carilli}, {DeBoer}, {Hewitt}, {Jacobs}, {McQuinn}, {Morales},
  {Parsons}, {Tegmark}, \& {Werthimer}}]{pob14}
{Pober}, J.~C., {Liu}, A., {Dillon}, J.~S., {et~al.} 2014, \apj, 782, 66

\bibitem[{{Santos} {et~al.}(2005){Santos}, {Cooray}, \& {Knox}}]{san05}
{Santos}, M.~G., {Cooray}, A., \& {Knox}, L. 2005, \apj, 625, 575

\bibitem[{{Scott} \& {Rees}(1990)}]{sco90}
{Scott}, D., \& {Rees}, M.~J. 1990, \mnras, 247, 510

\bibitem[{{Sunyaev} \& {Zeldovich}(1972)}]{sun72}
{Sunyaev}, R.~A., \& {Zeldovich}, Y.~B. 1972, \aap, 20, 189

\bibitem[{{Thompson} {et~al.}(2001){Thompson}, {Moran}, \& {Swenson}}]{tho01}
{Thompson}, A.~R., {Moran}, J.~M., \& {Swenson}, Jr., G.~W. 2001,
  {Interferometry and Synthesis in Radio Astronomy, 2nd Edition} (Wiley)

\bibitem[{{Thyagarajan} {et~al.}(2013){Thyagarajan}, {Udaya Shankar},
  {Subrahmanyan}, {Arcus}, {Bernardi}, {Bowman}, {Briggs}, {Bunton},
  {Cappallo}, {Corey}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
  {Hazelton}, {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper},
  {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter},
  {Mitchell}, {Morales}, {Morgan}, {Oberoi}, {Ord}, {Pathikulangara},
  {Remillard}, {Rogers}, {Anish Roshi}, {Salah}, {Sault}, {Srivani}, {Stevens},
  {Thiagaraj}, {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams},
  {Williams}, \& {Wyithe}}]{thy13}
{Thyagarajan}, N., {Udaya Shankar}, N., {Subrahmanyan}, R., {et~al.} 2013,
  \apj, 776, 6

\bibitem[{{Thyagarajan} {et~al.}(2015){Thyagarajan}, {Jacobs}, {Bowman},
  {Barry}, {Beardsley}, {Bernardi}, {Briggs}, {Cappallo}, {Carroll}, {Corey},
  {de Oliveira-Costa}, {Dillon}, {Emrich}, {Ewall-Wice}, {Feng}, {Goeke},
  {Greenhill}, {Hazelton}, {Hewitt}, {Hurley-Walker}, {Johnston-Hollitt},
  {Kaplan}, {Kasper}, {Kim}, {Kittiwisit}, {Kratzenberg}, {Lenc}, {Line},
  {Loeb}, {Lonsdale}, {Lynch}, {McKinley}, {McWhirter}, {Mitchell}, {Morales},
  {Morgan}, {Neben}, {Oberoi}, {Offringa}, {Ord}, {Paul}, {Pindor}, {Pober},
  {Prabu}, {Procopio}, {Riding}, {Rogers}, {Roshi}, {Udaya Shankar}, {Sethi},
  {Srivani}, {Subrahmanyan}, {Sullivan}, {Tegmark}, {Tingay}, {Trott},
  {Waterson}, {Wayth}, {Webster}, {Whitney}, {Williams}, {Williams}, {Wu}, \&
  {Wyithe}}]{thy15}
{Thyagarajan}, N., {Jacobs}, D.~C., {Bowman}, J.~D., {et~al.} 2015, ArXiv
  e-prints, arXiv:1502.07596
